Impact of Roe v. Wade’s Overturn: Abortion Restrictions and Infant Mortality in the U.S. Using a Difference-in-Differences Analysis

### 2024-12-06 paper/ExaminingtheimpactOverturnofRoev.Wade:BanningofAbortiononInfantMortalityRatesintheUnitedStatesUsingaDifference-in-DifferencesApproach.qmd
fix typo error

One model includes control variables — Age of Mother,
Mother's Single Race, and Year of Death to adjust for confounders
that may influence infant death rates. This adjustment addresses
compositional differences assumed in the DID framework and ensures
unbiased estimates of the intervention’s effect. The second model
excludes these controls to focus on the overall intervention impact,
avoid overfitting, and prioritize simplicity where variability is
adequately accounted for by design or random effects. By fitting two
models, we compare outcomes to refine estimates and evaluate the direct
impact of the intervention.

>>>>

The first model
excludes these controls to focus on the overall intervention impact,
avoid overfitting, and prioritize simplicity where variability is
adequately accounted for by design or random effects. The second model includes control variables — Age of Mother,
Mother's Single Race, and Year of Death to adjust for confounders
that may influence infant death rates. This adjustment addresses
compositional differences assumed in the DID framework and ensures
unbiased estimates of the intervention’s effect. By fitting two
models, we compare outcomes to refine estimates and evaluate the direct
impact of the intervention.
